From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-06 paper.tex
Tweak RTNeuron section

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor Zero-Buf}

@@

RTNeuron is the oldest of our interactive visualization tools. Originally
conceived as a standalone application for visualizing simulation results, it
has evolved into a rasterization-based rendering engine library implemented in
C++ with a Python wrapping. The power of RTNeuron lies in a domain specific API
designed for the visualization of detailed neuronal circuit models, this API
allows for building custom applications tailored for specific use cases.
It provides features to visualize static circuit data and some simulation
results. Static data visualization includes different visual representations for
neurons, synapses, selective pruning of neuronal trees, clipping
planes... The simulation results that can be displayed are the spiking
activity of the neurons and scalar variables from the cable models mapped to
the neuron surface. The color maps for displaying these data are highly
configurable, being posible to apply different color maps to different cell
subsets.

@@

The core engine is implemented in C++ using Equalizer and OpenSceneGraph and
also leverages part of our messaging framework to allow coupling with other
applications. The 3D view can be embedded inside Qt applications, in particular
in Python with PyQt and QML for overlaying GUI elements. Several use-case
specific applications have been built this way.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor Zero-Buf ras-te-ri-za-tion}

@@

RTNeuron\cite{Hernando13} is the oldest of our interactive visualization tools.
Originally conceived as a standalone application for visualizing simulation
results, it has evolved into a rasterization-based rendering engine library
implemented in C++ with a Python wrapping. The power of RTNeuron lies in a
domain specific API designed for the visualization of detailed neuronal circuit
models, this API allows for building custom applications tailored for specific
use cases. It provides features to visualize static circuit data and some
simulation results. Static data visualization includes different visual
representations for neurons, synapses, selective pruning of neuronal trees,
clipping planes and others. The simulation results that can be displayed are the
spiking activity of the neurons and scalar variables from the cable models
mapped to the neuron surface. The color maps for displaying these data are
highly configurable, allowing to apply different color maps to different cell
subsets.

@@

The core engine is implemented in C++ using Equalizer and OpenSceneGraph and
leverages part of our messaging framework to allow coupling with other
applications. The 3D view can be embedded inside Qt applications, in particular
in Python with PyQt and QML for overlaying GUI elements. Several use case
specific applications have been built this way.
